### 2016-02-18 ch02-qlogms/excitation-design.tex
Add epigraphs
Some small changes all over the place
Ch02: merge conclusion

\chapter{Design of excitation signals}
\label{sec:excitation}
\def\thisDir{ch02-qlogms}
\researchBasedOn{Geerardyn2012IMTC, Geerardyn2013TIM, Larsson2012SYSID}

@@

  \begin{table}
  \centering
   \caption{Summary of  properties of the different frequency grids.}
    \begin{tabular}{rccc} 
    \toprule
    Grid & Linear & Logarithmic & Quasi-logarithmic \\
    \midrule
    % Limits & \multicolumn{3}{c}{$\ClosedInterval{\fMin, \fMax}$}\\
    Properties 
       & $f_0, \Delta f$ 
       & $f_0, \alpha$ 
       & $f_0, \Delta f, \alpha$\\
    \midrule
    $f_{k+1} \isdef$ 
       & $f_{k} + \Delta f$ 
       & $\alpha f_{k}$
       & $\round{\frac{\alpha^{N_k} f_k}{\Delta f}} \Delta f$,   $N_k \in \NaturalNumbers$
       \\[5pt]
    $\Delta f_k \isdef f_{k+1} - f_k$ 
       & $\Delta f$
       & $(\alpha - 1) f_k$
       & $ \in \NaturalNumbersWithoutZero \Delta f$ \\[5pt]
    $\alpha_k \isdef \frac{f_{k+1}}{f_k}$ 
       & $1 + \frac{\Delta f}{f_k}$ 
       & $\alpha$ 
       & $\approx \alpha $ \\[5pt]
    $F_{\ClosedInterval{a,b}}$
       & $\floor{\frac{b - a}{\Delta f}}$
       & $\floor{\log_{\alpha} \frac{b}{a}}$
       & $\approx \floor{\log_{\alpha} \frac{b}{a}}$\\[5pt]
    $F_{\ClosedInterval{f, \kappa f}}$
      & $\floor{\frac{(\kappa - 1)f}{\Delta f}}$
      & $\floor{\log_{\alpha} \kappa}$
      & $\approx \floor{\log_{\alpha} \kappa}$\\[5pt]
    \bottomrule
    \end{tabular}
  \end{table}

@@

\section{Simulations} \label{sec:simulation}
In the following set of simulations, we will study how the FRF of different second order systems with equal damping (and the corresponding uncertainty) are measured by the multisine excitation signals from Section~\ref{sec:method}.
  \subsection{Setup}
  We consider second-order systems with an equal damping and with resonance frequencies $4$, $8$, $20$, $40$, $80$, $200$, $400$, $800$, $2000$ and $4000 \unit{Hz}$.
  Using the \matlab\ instruction \texttt{cheby1}, discrete-time equivalents of these systems are generated.
  These can be represented by a transfer function of the form:
  \begin{equation}
    G \left( z \right)\Big|_{\damping, \fR} =
       \frac{         b_2  z^{2} + b_1 z + b_0}%
            {\phantom{a_2} z^{2} + a_1 z + a_0}
  \text{.}
  \label{eq:excitation:secondOrderSystemDTidentifiable}
  \end{equation}

@@

\section{Conclusion}
\label{sec:excitation:conclusion}
In this chapter we have illustrated that quasi-logarithmic multisine excitations are a well-suited to measure transfer functions over broad frequency ranges with a constant relative uncertainty of the present resonances.

The suggested amplitude compensation methods allow the user to measure a parametric \gls{LTI} model for systems in a wide frequency band with a constant uncertainty.
The variance of the estimates at lower frequencies is improved in comparison to the uncompensated case at the cost of a slightly increased (yet constant) variance at higher frequencies for excitation signals with an equal power content.
In practical applications, this slight increase is likely to be negligible.
The suggested compensation works well as long as the considered systems are sufficiently damped with respect to the density of the excited frequency lines.

>>>>

\chapter{Design of excitation signals}
\label{sec:excitation}
\def\thisDir{ch02-qlogms}
\myEpigraph{A common mistake that people make when trying to design something completely foolproof is to underestimate the ingenuity of complete fools.}{Douglas Adams}{Mostly Harmless}
\researchBasedOn{Geerardyn2012IMTC, Geerardyn2013TIM, Larsson2012SYSID}

@@

  \begin{table}
  \centering
   \caption{Summary of  properties of the different frequency grids.}
    \begin{tabular}{rccc} 
    \toprule
     & \textsc{Linear} & \textsc{Logarithmic} & \textsc{Quasi-logarithmic} \\
    \midrule
    % Limits & \multicolumn{3}{c}{$\ClosedInterval{\fMin, \fMax}$}\\
    Properties 
       & $f_0, \Delta f$ 
       & $f_0, \alpha$ 
       & $f_0, \Delta f, \alpha$\\
    \midrule
    $f_{k+1} \isdef$ 
       & $f_{k} + \Delta f$ 
       & $\alpha f_{k}$
       & $\round{\frac{\alpha^{N_k} f_k}{\Delta f}} \Delta f$,   $N_k \in \NaturalNumbersWithoutZero$
       \\[5pt]
    $\Delta f_k \isdef f_{k+1} - f_k$ 
       & $\Delta f$
       & $(\alpha - 1) f_k$
       & $ \in \NaturalNumbersWithoutZero \Delta f$ \\[5pt]
    $\alpha_k \isdef \frac{f_{k+1}}{f_k}$ 
       & $1 + \frac{\Delta f}{f_k}$ 
       & $\alpha$ 
       & $\approx \alpha $ \\[5pt]
    $F_{\ClosedInterval{a,b}}$
       & $\floor{\frac{b - a}{\Delta f}}$
       & $\floor{\log_{\alpha} \frac{b}{a}}$
       & $\approx \floor{\log_{\alpha} \frac{b}{a}}$\\[5pt]
    $F_{\ClosedInterval{f, \kappa f}}$
      & $\floor{\frac{(\kappa - 1)f}{\Delta f}}$
      & $\floor{\log_{\alpha} \kappa}$
      & $\approx \floor{\log_{\alpha} \kappa}$\\[5pt]
    \bottomrule
    \end{tabular}
  \end{table}

@@

\section{Simulations} \label{sec:excitation:simulation}
In the following set of simulations, we will study how the FRF of different second order systems with equal damping (and the corresponding uncertainty) are measured by the multisine excitation signals from Section~\ref{sec:method}.
  \subsection{Setup}
  We consider second-order systems with an equal damping and with resonance frequencies $4$, $8$, $20$, $40$, $80$, $200$, $400$, $800$, $2000$ and $4000 \unit{Hz}$.
  Using the \matlab\ instruction \texttt{cheby1}, discrete-time equivalents of these systems are generated.
  These can be represented by a transfer function of the form:
  \begin{equation}
    G \left( z \right)\Big|_{\damping, \fR} =
       \frac{         b_2  z^{2} + b_1 z + b_0}%
            {\phantom{a_2} z^{2} + a_1 z + a_0}
  \text{.}
  \label{eq:excitation:secondOrderSystemDTidentifiable}
  \end{equation}

@@

\section{Conclusion}
\label{sec:excitation:conclusion}
In this chapter, we recalled that the design of optimal excitation signals may require prior knowledge that is either not sufficiently accurate or even unavailable.
When only the limited prior knowledge that the system resonances lie in a certain (possibly very wide) frequency band, a suitable class of excitation signals can be constructed such that the relative uncertainty of the estimated resonance is independent of the resonance frequency.
We showed that such a signal should have a power spectrum that is distributed in $1/f$.

In this chapter we have illustrated that quasi-logarithmic multisine excitations are a well-suited to measure transfer functions over broad frequency ranges with a constant relative uncertainty of the present resonances.
The suggested amplitude compensation methods allow the user to measure a parametric \gls{LTI} model for systems in an even wider frequency band with a constant uncertainty.
The variance of the estimates at lower frequencies is improved in comparison to the uncompensated case at the cost of a slightly increased (yet constant) variance at higher frequencies for excitation signals with an equal power content.
In practice, this slight increase is likely to be negligible.
The suggested compensation works well as long as the considered systems are sufficiently damped with respect to the density of the excited frequency lines.

### 2016-02-18 ch02-qlogms/sysid.tex
Some small changes all over the place
Ch02: merge conclusion

Second, we consider the power spectrum of the quasi-logarithmic multisine signal [\cite{Pintelon2012}] given by
\begin{align}
  \phi_u(\omega) &= \frac{1}{M}\sum_{k=1}^{M}{\delta(\omega,\wn[K])},
\end{align}
where $\omega_{k}/\omega_{k+1} \approx \alpha = e^{\Delta}$.
Hence, the number of spectral lines inside \wdB is 
\begin{align}
  \floor{
    \log_{\alpha} \frac{1+\damping}{1-\damping} 
  }
  \text{,}
\end{align}
where $\floor{\placeholder}$ is the nearest integer rounded towards $0$. The number of spectral lines is independent of $\wn$.

@@

The result of these two choices of input power spectrum is that for a given damping, $\var{\hat{G}}$ is approximately the same independent of $\wn$. 
This is illustrated in \secref{sec:excitation:sim}.

@@

%%Conclusion
\section{Conclusions}\label{sec:excitation:conclusions}
In this paper we recalled that the design of an optimal excitation signal may require prior system knowledge that is insufficiently accurate or even unavailable. 
When only the limited prior knowledge that the system resonances lie in a certain (possibly wide) frequency band, we can create a suitable class of excitation signals. 
These signals are required to yield estimates having a variance that is independent of the resonance frequencies of the system. 
We showed that such a signal should have a power spectrum that is distributed in $1/f$.
In this paper (quasi-)logarithmic multisines were considered to serve this purpose.

By means of simulations for different second order sub-systems, it is confirmed that for a given damping, the variance of the estimated is almost independent of the actual resonance frequencies of the system within the frequency band of interest.
The same results were found for higher order systems and illustrated for an example. 
A theoretical motivation for these results is provided.

The proposed excitation signals therefore offer an easy and efficient way to identify systems in a wide frequency range such that an accuracy level that is independent of the resonance frequencies can be attained for the complete frequency span.

>>>>

Second, we consider the power spectrum of the quasi-logarithmic multisine signal [\cite{Pintelon2012}] given by
\begin{align}
  \phi_u(\omega) &= \frac{1}{M}\sum_{k=1}^{M}{\delta(\omega,\wn[K])},
\end{align}
where $\omega_{k}/\omega_{k+1} \approx \alpha$.
Hence, the number of spectral lines inside \wdB is 
\begin{align}
  \floor{
    \log_{\alpha} \frac{1+\damping}{1-\damping} 
  }
  \text{,}
\end{align}
where $\floor{\placeholder}$ is the nearest integer rounded towards $0$. The number of spectral lines is independent of $\wn$.

@@

The result of these two choices of input power spectrum is that for a given damping, $\var{\hat{G}}$ is approximately the same independent of $\wn$. 
This is illustrated in \secref{sec:excitation:simulation}.

@@
